Paper 1

### 2022-06-08 scripts/Paper 1.Rmd
u

@@

ER.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()
```

>>>>

Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.mean = mean(Ts.mean))

@@

ER.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()

Ts.summary %>%
  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()
```
